On the specific recursive structure of iterated parametricity

### 2025-11-16 paper/paper.tex
paper: minor corrections
Use again n instead of n-p in tables

\begin{equation*}
  \begin{tikzcd}
    X_0: \U & X_1: \U \arrow[l, "\partial^L" description, shift left=2] \arrow[l, "\partial^R" description, shift right=2] & X_2: \U \arrow[l, "\partial^{L\kstar}" description, shift left=6] \arrow[l, "\partial^{R\kstar}" description, shift left=2] \arrow[l, "\partial^{\kstar L}" description, shift right=2] \arrow[l, "\partial^{\kstar R}" description, shift right=6] & \ldots
  \end{tikzcd}
\end{equation*}
we consider a family of families as shown below:
\begin{equation*}
  \begin{array}{lll}
    X_0 & :               \U                                                                          \\
    X_1 & :               X_0 \times X_0 \rightarrow  \U                                              \\
    X_2 & : \Pi a b c d.\,  X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
    \ldots
  \end{array}
\end{equation*}

@@

In the current paper and associated formalisation, we switch the point
of view, take $\framep[n-2][p]$ $\painting[n-2][p]$, $\restrf[n-1][p]$
and $\restrp[n-1][p]$ as references and renaming them respectively as
$\framep[n][p]$, $\painting[n][p]$, $\restrf[n][p]$ and
$\restrp[n][p]$, replace the equational properties of $\framep[n][p]$,
$\framep[n-1][p]$, $\restrf[n][p]$, $\painting[n][p]$,
$\painting[n-1][p]$ and $\restrp[n][p]$ as definitions of objects
respectively renamed to $\framep[n+2][p]$, $\framep[n+1][p]$,
$\restrf[n+1][p]$, $\painting[n+2][p]$, $\painting[n+1][p]$ and
$\restrp[n+1][p]$, building instead by induction a block of the form:

@@

              \restrp[n+1][p](\depscoht.\fulldepscohs[n][0,...,n])              \\

@@

    (\unitpoint)                                                     & \defeq                                            & (\unitpoint,\lambda q.\lambda r. \lambda\epsilon. \lambda\omega.\lambda \_.\refl)                               \\

@@

              (
              \fulldepscoht[n])(d)(l))                                           \\

@@

Indeed, to build this structure at level $n+1$, from level $n$, it is
enough to assume $E:\framep[n+1][n](\deps[n]) \rightarrow \U$ (where
$\deps[n]$ come from the assumptions at level $n$) and to build the
following:
\begin{itemize}
  \item $\framep[n+1][0,...,n]$ comes from $\deps[n]$ which holds by assumptions (using $\framep[n][0,...,n-1]$, $\painting[n][0,...,n-1]$ and $\restrf[n][0,...,n-1]$)
  \item $\painting[n+1][0,...,n]$ comes from $\fulldeps[n]$ which holds by assumptions (also using $E$)
  \item $\restrf[n+1][0,...,n]$ comes from $\depscohs[n][0,...,n-1]$ which holds by assumptions (additionally using the assumptions of $\restrp[n][0,...,n-1]$ and $\cohf[n][0,...,n-1]$)
  \item $\restrp[n+1][0,...,n]$ assuming $E':\framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$ comes from $\fulldepscohs[n][0,...,n-1]$ which holds by assumptions (additionally using $E'$)
  \item $\cohf[n+1][0,...,n]$ assuming $E'$ comes from $\depscoht[n][0,...,n-1]$ which holds by assumptions (additionally using the assumption of $\cohp[n][0,...,n-1]$ and proving $\coht[n][0,...,n-1]$ by uniqueness of identity proofs)
  \item $\cohp[n+1][0,...,n]$ assuming $E'$ and $E'': \framep[n+3][n+2](\overline{\deps}(\overline{\depscohs}(\depscoht[n][0,...,n-1]))) \rightarrow \U$ comes from $\fulldepscoht[n][0,...,n-1]$ which holds by assumptions (additionally using $E''$)
\end{itemize}

>>>>

\begin{equation*}
  \begin{tikzcd}
    X_0: \U & X_1: \U \arrow[l, "\partial^L" description, shift left=2] \arrow[l, "\partial^R" description, shift right=2] & X_2: \U \arrow[l, "\partial^{L\kstar}" description, shift left=6] \arrow[l, "\partial^{R\kstar}" description, shift left=2] \arrow[l, "\partial^{\kstar L}" description, shift right=2] \arrow[l, "\partial^{\kstar R}" description, shift right=6] & \ldots
  \end{tikzcd}
\end{equation*}
we consider a family of families as shown below:
\begin{equation*}
  \begin{array}{lll}
    E_0 & :               \U                                                                          \\
    E_1 & :               E_0 \times X_0 \rightarrow  \U                                              \\
    E_2 & : \Pi a b c d.\,  E_1(a,b) \times E_1 (c,d) \times E_1(a,c) \times E_1 (b,d) \rightarrow \U \\
    \ldots
  \end{array}
\end{equation*}

@@

In the current paper and associated formalisation, we switch the point
of view, take $\framep[n-2][p]$ $\painting[n-2][p]$, $\restrf[n-1][p]$
and $\restrp[n-1][p]$ as references and rename them respectively as
$\framep[n][p]$, $\painting[n][p]$, $\restrf[n][p]$ and
$\restrp[n][p]$. We replace the equational properties of $\framep[n][p]$,
$\framep[n-1][p]$, $\restrf[n][p]$, $\painting[n][p]$,
$\painting[n-1][p]$ and $\restrp[n][p]$ with definitions, renaming them
respectively to $\framep[n+2][p]$, $\framep[n+1][p]$,
$\restrf[n+1][p]$, $\painting[n+2][p]$, $\painting[n+1][p]$ and
$\restrp[n+1][p]$. This means that we build instead by induction a block of the form:

@@

              \restrp[n+1][p](\depscoht.\fulldepscohs[n])                       \\

@@

    \unitpoint                                                       & \defeq                                            & (\unitpoint,\lambda q.\lambda r. \lambda\epsilon. \lambda\omega.\lambda \_.\refl)                               \\

@@

              (\fulldepscoht[n])(d)(l))                                          \\

@@

Indeed, to build this structure at level $n+1$, from level $n$, it is
enough to assume $E:\framep[n+1][n](\deps[n]) \rightarrow \U$ (where
$\deps[n]$ come from the assumptions at level $n$) and to build the
following:
\begin{itemize}
  \item $\framep[n+1][0,...,n]$ comes from $\deps[n]$ which holds by assumptions (using $\framep[n][0,...,n-1]$, $\painting[n][0,...,n-1]$ and $\restrf[n][0,...,n-1]$)
  \item $\painting[n+1][0,...,n]$ comes from $\fulldeps[n]$ which holds by assumptions (also using $E$)
  \item $\restrf[n+1][0,...,n]$ comes from $\depscohs[n][0,...,n-1]$ which holds by assumptions (additionally using the assumptions of $\restrp[n][0,...,n-1]$ and $\cohf[n][0,...,n-1]$)
  \item $\restrp[n+1][0,...,n]$ assuming $E':\framep[n+2][n+1](\overline{\deps}(\depscohs[n][0,...,n-1])) \rightarrow \U$ comes from $\fulldepscohs[n]$ which holds by assumptions (additionally using $E'$)
  \item $\cohf[n+1][0,...,n]$ assuming $E'$ comes from $\depscoht[n][0,...,n-1]$ which holds by assumptions (additionally using the assumption of $\cohp[n][0,...,n-1]$ and proving $\coht[n][0,...,n-1]$ by uniqueness of identity proofs)
  \item $\cohp[n+1][0,...,n]$ assuming $E'$ and $E'': \framep[n+3][n+2](\overline{\deps}(\overline{\depscohs}(\depscoht[n][0,...,n-1]))) \rightarrow \U$ comes from $\fulldepscoht[n][0,...,n-1]$ which holds by assumptions (additionally using $E''$)
\end{itemize}
